\documentclass{article}
\usepackage{ctex}
\usepackage{amsmath, amsthm, amssymb, amsfonts}
\usepackage{thmtools}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{geometry}
\usepackage{array}
\usepackage{float}
\usepackage{pxfonts}
\usepackage{rotating}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{framed}
\usepackage[dvipsnames]{xcolor}
\usepackage{tcolorbox}
\usepackage[T1]{fontenc}
\usepackage{appendix}
\usepackage{tikz-cd}
\usepackage{blindtext}
\colorlet{LightGray}{White!90!Periwinkle}
\colorlet{LightOrange}{Orange!15}
\colorlet{LightGreen}{Green!15}
\newtheorem{example}{Example}[section]
\newtheorem{problem}{Exercise}[section]
\newtheorem{note}{Remark}[section]
\newtheorem{lemma}{Lemma}[section]
\newcommand{\HRule}[1]{\rule{\linewidth}{#1}}
\pagenumbering{roman}
\declaretheoremstyle[name=Theorem,]{thmsty}
\declaretheorem[style=thmsty,numberwithin=section]{theorem}
\tcolorboxenvironment{theorem}{colback=LightGray}

\declaretheoremstyle[name=Proposition,]{prosty}
\declaretheorem[style=prosty,numberlike=theorem]{proposition}
\tcolorboxenvironment{proposition}{colback=LightGray}

\declaretheoremstyle[name=Principle,]{prcpsty}
\declaretheorem[style=prcpsty,numberlike=theorem]{principle}
\tcolorboxenvironment{principle}{colback=LightGray}

\declaretheoremstyle[name=Definition,]{defsty}
\declaretheorem[style=defsty,numberlike=theorem]{definition}
\tcolorboxenvironment{definition}{colback=LightGray}

\declaretheoremstyle[name=Axiom,]{defsty}
\declaretheorem[style=defsty,numberlike=theorem]{axiom}
\tcolorboxenvironment{axiom}{colback=LightGray}

\declaretheoremstyle[name=Corollary,]{defsty}
\declaretheorem[style=defsty,numberlike=theorem]{corollary}
\tcolorboxenvironment{corollary}{colback=LightGray}

\setstretch{1.2}
\geometry{
    textheight=9in,
    textwidth=5.5in,
    top=1in,
    headheight=12pt,
    headsep=25pt,
    footskip=30pt
}
\usepackage{tikz}
% -----------------------------------------------------------------------------

\begin{document}

% -----------------------------------------------------------------------------
% Cover Page and ToC
% -----------------------------------------------------------------------------

\title{ \normalsize \textsc{}
		\\ [2.0cm]
		\HRule{1.5pt} \\
		\LARGE \textbf{\uppercase{Algebra}
		\HRule{2.0pt} \\ [0.6cm] \LARGE{Abstract and Commutative Algebra} \vspace*{10\baselineskip}}
		}
\date{\today}
\author{\textbf{Author} \\ 
		Clarigatio \\
		}

\maketitle
\newpage

\tableofcontents
\newpage
% -----------------------------------------------------------------------------
\section*{Preface}
This book introduces concepts from basic algebra, which traditionally has been characterized as including abstract algebra and part of commutative algebra. In the abstract algebra section, we first introduce some basic concepts from set theory and logic, and then discuss them in the order of group theory, ring theory, and field theory. The content of this section overlaps with the first five chapters of Hungerford's \textit{Algebra}. Subsequently, for the section on commutative algebra, we introduce the language of schemes in the exercises, which helps the reader to make a better connection between commutative algebra and algebraic geometry. In the main text of this section we focus on localization theory, primitive decompositions of rings, integral dependence and valuation rings. The contents of this section overlap with the first five chapters of Atiyah's book \textit{An Introduction to Commutative Algebra}. Most of the exercises in the two main reference books have been solved. Those that are not answered are either trivial, too complicated (but not too difficult), or too difficult. In the appendix, we present a little bit of homological algebra, which is only useful for a very few of Atiyah's post-training exercises, and so we place it at the back of the book for the interested reader. It is worth noting that this section is not an obstacle to understanding the book even if it is not mastered now, but we recommend that the reader read it in its entirety, since the homological method plays a very important role in modern algebraic research. Due to the author's limited level, there are inevitable mistakes or errors in the text, and I urge readers to criticise and correct them.\par
Below we list some of the main references of this book.
[1] Artin: \textit{Algebra}.\par
[2] Derek J.S. Robinson: \textit{A Course in the Theory of Groups}.\par
[3] Dummit and Foote: \textit{Abstract Algebra}.\par
[4] Joseph J. Rotman: \textit{An Introduction to the Theory of Groups}.\par
[5] David Eisenbud: \textit{Commutative Algebra: With a View Towards Algebraic Geometry}.\par
[6] O.Zariski and P.Samuel, \textit{Commutative Algebra} volume I and II.\par
[7] Gregor Kemper, \textit{A Course in Commutative Algebra}.\par
[8] A. Grothendieck, \textit{Elements of Algebraic Geometry}.\par
[9] Gerald J. Janusz, \textit{Algebraic Number Fields}.\par
[10] Jurgen Neukirch, \textit{Algebraic Number Theory}.\par
[8] 李文威: \textit{代数学方法: 基础架构}.\par
[9] 丁石孙, 聂灵沼: \textit{代数学引论}.
\begin{flushright}
    \begin{tabular}{c}
        Clarigatio\\
        \today
    \end{tabular}
\end{flushright}
\newpage
\pagenumbering{arabic}
\part{Abstract Algebra}
\newpage
\part{Commutative Algebra}
\input{Commutative Algebra/Integral Dependence and Valuations}
\newpage
\end{document}